---
title: "Sensitivity analysis: linear model"
author: "Dani Cosme"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    highlight: tango
    theme: united
    toc: true
    toc_float: 
      collapsed: TRUE
      smooth_scroll: TRUE
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.path = "figs_linear/")

options(scipen = 999)
```

This document provides the code for the analyses reported in:

[Cosme et al. (Preprint) Testing the adolescent social reorientation model using hierarchical growth curve modeling with parcellated fMRI data](https://psyarxiv.com/8eyf5/)

This script reproduces the analyses reported in the main manuscript but estimating only linear relationships with age (i.e., removing the quadratic terms).

# load packages
```{r}
library(tidyverse)
library(knitr)
library(lme4)
library(lmerTest)
```

# define color palettes and labels
```{r}
pal_self_other = c("#FFA90A", "#247BA0")
pal_social_academic = c("#63647E", "#F25F5C")
pal_wave = c("#693668", "#A74482", "#F84AA7")
pal_label = c("#47A8BD", "#DBC057", "#FF3366")
pal_gender = c("#70c1b3","#247BA0")

parcel_labeller = labeller(label = c('social' = 'social parcels', 'other' = 'control parcels', 'self' = 'self parcels'),
                           domain = c('social' = 'social domain', 'academic' = 'academic domain'),
                           wave = c("t1" = "wave 1", "t2" = "wave 2", "t3" = "wave 3"))

label_df = expand.grid(label = c("social", "self", "other"),
              target = c("self", "other"),
              domain = c("social", "academic"),
              age = 13,
              expected_avg = 1,
              expected_diff = 1)

dcbw = theme_classic() +
  theme(text = element_text(size = 14, family = "Futura Medium", color = "black"),
        panel.background = element_blank(),
        plot.background = element_blank(),
        strip.background = element_blank(),
        strip.text = element_text(size = 14),
        legend.background = element_rect(fill = NA, color = NA),
        axis.line = element_line(color = "black"),
        axis.text = element_text(color = "black"),
        panel.grid.minor = element_blank())
```

# load MRI data

-   exclude participants with \>20% volumes with motion artifacts or low quality FX data
-   standardize betas within parcel (across participants and time)
-   recode standardized betas +/- 3 SDs from the mean as NA (0.8% of all observations)

```{r}
# define parcels
self_parcels = c(5, 17, 28, 47, 52, 66, 116, 147, 152, 156, 184, 198, 207, 225, 249, 292, 309, 354, 380)
social_parcels = c(18, 23, 29, 49, 54, 59, 62, 63, 67, 76, 111, 114, 139, 143, 146, 150, 178, 179, 189, 203, 212, 224, 229, 236, 238, 239, 245, 250, 259, 266, 271, 301, 305, 310, 322, 324, 328, 331, 333, 342, 343, 350, 374, 391)

# mri exclusions
mri_exclusions = c('s002_t1', 's004_t1', 's008_t1', 's011_t1', 's017_t1', 
                   's026_t1', 's033_t2', 's034_t1', 's041_t1', 's044_t1', 
                   's047_t1', 's051_t1', 's054_t1', 's057_t1', 's059_t1', 
                   's061_t1', 's063_t1', 's070_t2', 's074_t1', 's074_t2', 
                   's078_t1', 's084_t1', 's090_t2', 's090_t3', 's094_t1', 
                   's094_t2', 's096_t1') 

# load and tidy parcel data
parcellations = read_csv('../data/fxParcellations.csv') %>%
  mutate(label = ifelse(parcellation %in% self_parcels, 'self',
                 ifelse(parcellation %in% social_parcels, 'social', 'other'))) %>%
  mutate(wave = paste0("t", as.numeric(c(`10` = 1, `13` = 2, `16` = 3)[as.character(age)]))) %>%
  select(-age) %>%
  unite(sub_wave, c(subjectID, wave), remove = FALSE) %>%
  group_by(parcellation) %>%
  mutate(inclusion = ifelse(sub_wave %in% mri_exclusions, "excluded from MRI", "completed MRI"),
         beta = ifelse(sub_wave %in% mri_exclusions, NA, beta),
         sd = ifelse(sub_wave %in% mri_exclusions, NA, sd),
         beta_std = scale(beta, center = FALSE, scale = TRUE),
         mean_beta_std = mean(beta_std, na.rm = TRUE)) %>%
    select(-sub_wave) %>%
  ungroup()

# exclude parameter estimates 3 SD from the mean
parcellations_ex = parcellations %>%
  mutate(beta_std = ifelse(beta_std > mean_beta_std + 3 | beta_std < mean_beta_std - 3, NA, beta_std))
```

# load demographic data and merge
```{r}
# demographics
demo = read.csv("../data/SFIC_age.pds.gender.csv") %>%
  rename("subjectID" = SID,
         "wave" = wavenum,
         "gender" = Gender) %>%
  mutate(subjectID = sprintf("s%03d", subjectID),
         wave = paste0("t", wave),
         age_c = age - 13,
         age_c2 = age_c^2,
         pdss_c = pdss - 3,
         pdss_c2 = pdss_c^2)

# merge data
merged = parcellations_ex %>%
  full_join(., demo, by = c("subjectID", "wave")) %>%
  mutate(inclusion = ifelse(is.na(inclusion), "didn't complete MRI", inclusion)) %>%
  filter(!(subjectID == "s086" & wave == "t3")) #no MRI, task, or self-report data was collected

# subset data for modeling
neuro_model_data = merged %>%
  filter(!is.na(beta)) %>%
  select(subjectID, wave, age, age_c, age_c2, target, domain, parcellation, label, beta, beta_std)

neuro_model_data_ex = neuro_model_data  %>%
  na.omit()

# dummy code target and domain
neuro_model_data_dummy = neuro_model_data_ex %>%
  mutate(target = ifelse(target == "self", .5, -.5),
         domain = ifelse(domain == "social", .5, -.5))
```

# run domain x target x age model {.tabset}
```{r}
# specify model
model_target_equation = formula(beta_std ~ 1 + age_c*target*domain*label +
                                  (1 + age_c*target*domain | subjectID) +
                                  (1 + age_c*target*domain | parcellation))

# calculate max number of iterations
model_target_formula = lFormula(model_target_equation, data = neuro_model_data_dummy)

model_target_numFx = length(dimnames(model_target_formula$X)[[2]])

model_target_numRx = sum(as.numeric(lapply(model_target_formula$reTrms$cnms, function(x) {
  l <- length(x)
  (l*(l - 1)) / 2 + l
})))

model_target_maxfun = 10*(model_target_numFx + model_target_numRx + 1)^2

# run or load the model
if (file.exists("../data/model_target_linear.RDS")) {
  model_target = readRDS("../data/model_target_linear.RDS")
} else {
  model_target = lmer(model_target_equation, data = neuro_model_data_dummy, REML = F, #Use ML since we want to compare random effects
                      verbose = 2,
                      control = lmerControl(optCtrl = list(maxfun = model_target_maxfun), optimizer = "bobyqa", calc.derivs = FALSE))
  saveRDS(model_target, "../data/model_target_linear.RDS")
}
```

# summarize model
```{r}
model_target %>%
  broom.mixed::tidy(effects = c("ran_pars", "fixed"), conf.int = TRUE) %>%
  filter(effect == "fixed") %>%
  select(-group) %>%
  rename("b" = estimate,
         "SE" = std.error,
         "t" = statistic,
         "p" = p.value) %>%
  mutate(p = round(p, 3),
         p = ifelse(p == 0, "< .001", gsub("0.(.*)", ".\\1", sprintf("%.3f", p))),
         term = gsub("\\(Intercept\\)", "Intercept (age 13, label (control))", term),
         term = gsub("target", "Target", term),
         term = gsub("domain", "Domain", term),
         term = gsub("labelself", "Label (self)", term),
         term = gsub("labelsocial", "Label (social)", term),
         term = gsub("age_c", "Age", term),
         term = gsub(":", " x ", term),
         term = gsub("sd__", "", term),
         term = gsub("Observation", "observation", term),
         effect = gsub("ran_pars", "random", effect),
         `b [95% CI]` = ifelse(effect == "fixed", sprintf("%.3f [%.3f, %.3f]", b, conf.low, conf.high), "--")) %>%
  mutate_if(is.numeric, round, 3) %>%
  mutate_if(is.numeric, funs(ifelse(is.na(.), "--", .))) %>%
  mutate_if(is.character, funs(ifelse(is.na(.), "--", .))) %>%
  select(term, `b [95% CI]`, SE, t, df, p) %>%
  kable(format = "pandoc")
```

# simple slopes {.tabset}
Estimate simple slopes to test interactions at specific levels

## run models
```{r}
# self social > academic
self_social = emmeans::emtrends(model_target, pairwise ~ domain,
                  var = "age_c", at = list(target =.5, label="social"),
                  lmerTest.limit = 188577)$contrasts %>%
  data.frame() %>%
  mutate(contrast = "self social > academic",
         parcel = "social",
         age_effect = "linear")

# social self > other
social_self = emmeans::emtrends(model_target, pairwise ~ target,
                  var = "age_c", at = list(domain =.5, label="self"),
                  lmerTest.limit = 188577)$contrasts %>%
  data.frame() %>%
  mutate(contrast = "social self > other",
         parcel = "self",
         age_effect = "linear")
```

## make table
```{r}
social_self %>%
  bind_rows(self_social) %>%
  select(contrast, parcel, age_effect, estimate, SE, df, t.ratio, p.value) %>%
  rename("b" = estimate,
         "t" = t.ratio,
         "p" = p.value) %>%
  mutate(b = round(b, 3) * -1, #flip signs for it's .5 - (-.5)
         SE = round(SE, 3),
         df = round(df, 2),
         t = abs(round(t, 2)),
         p = round(p, 3)) %>%
  kable(format = "pandoc")
```

# visualize fitted models {.tabset}
Visualize the developmental trajectory using the fitted values from the domain x target x age model

```{r}
reForm = as.formula("~(1 + age_c*target*domain | parcellation)")

neuro_plot_data = with(neuro_model_data_dummy, 
                    expand.grid(target = unique(target), 
                                domain = unique(domain),
                                parcellation = unique(parcellation),
                                age = unique(age),
                                stringsAsFactors = F)) %>%
  mutate(label = ifelse(parcellation %in% self_parcels, 'self',
                 ifelse(parcellation %in% social_parcels, 'social', 'other')),
         age_c = age - 13, 
         age_c2 = age_c^2, 
         subjectID = NA)
neuro_plot_data$expected = predict(model_target, newdata = neuro_plot_data, re.form = reForm)
neuro_plot_data$expected_mean = predict(model_target, newdata = neuro_plot_data, re.form = NA)

neuro_plot_data = neuro_plot_data %>%
  mutate(target = factor(target, levels = c(-.5, .5), labels = c("other", "self")),
         domain = factor(domain, levels = c(-.5, .5), labels = c("academic", "social")))
```

## hypothesis 0
```{r h0_fitted, fig.width=12, fig.height=5}
domain_parc_plot = neuro_plot_data %>%
  distinct(parcellation, target, domain, age, label, .keep_all = T) %>%
  group_by(subjectID, age, label, domain, parcellation) %>%
  mutate(expected_avg = mean(expected, na.rm = TRUE)) %>%
  ggplot(aes(x = age, y = expected_avg, color = domain)) + 
  geom_smooth(aes(group = interaction(parcellation, domain), size = label), method = "lm", formula = y ~ poly(x, 2), se = FALSE, show.legend = FALSE) +
  geom_smooth(method = "lm", formula = y ~ poly(x, 2), size = 1.25, se = FALSE) +
  scale_color_manual(name = "", values = pal_social_academic) +
  scale_size_manual(values = c(.05, .1, .1)) +
  scale_x_continuous(breaks = c(10, 13, 16)) + 
  scale_y_continuous(breaks = c(-1, 0, 1)) + 
  coord_cartesian(ylim = c(-1.2, 1.2)) +
  facet_grid(~label, labeller = parcel_labeller) +
  labs(x = "\nage", y = "mean predicted BOLD signal value\n") + 
  dcbw +
  theme(legend.position = c(.85, .15),
        legend.spacing.y = unit(.01, 'cm'),
        legend.margin = unit(0, "cm"))

target_parc_plot = neuro_plot_data %>%
  distinct(parcellation, target, domain, age, label, .keep_all = T) %>%
  group_by(subjectID, age, label, target, parcellation) %>%
  mutate(expected_avg = mean(expected, na.rm = TRUE)) %>%
  ggplot(aes(x = age, y = expected_avg, color = target)) + 
  geom_smooth(aes(group = interaction(parcellation, target), size = label), method = "lm", formula = y ~ poly(x, 2), se = FALSE, show.legend = FALSE) +
  geom_smooth(method = "lm", formula = y ~ poly(x, 2), size = 1.25, se = FALSE) +
  scale_color_manual(values = pal_self_other) +
  scale_size_manual(values = c(.05, .1, .1)) +
  scale_x_continuous(breaks = c(10, 13, 16)) + 
  scale_y_continuous(breaks = c(-1, 0, 1)) + 
  coord_cartesian(ylim = c(-1.2, 1.2)) +
  facet_grid(~label, labeller = parcel_labeller) +
  labs(x = "\nage", y = "mean predicted BOLD signal value\n", color = "") + 
  dcbw +
  theme(legend.position = c(.85, .15),
        legend.spacing.y = unit(.01, 'cm'),
        legend.margin = unit(0, "cm"))

(h0_fitted = cowplot::plot_grid(domain_parc_plot, target_parc_plot,
                                labels = c('A', 'B'), ncol = 2,
                                rel_widths = c(1, 1)))
```

## hypothesis 1
```{r h1_fitted, fig.width=12, fig.height=5}
domain_plot = neuro_plot_data %>%
  group_by(subjectID, age, label, domain, parcellation) %>%
  mutate(expected_avg = mean(expected_mean, na.rm = TRUE)) %>%
  distinct(parcellation, target, domain, age, label, .keep_all = T) %>%
  ggplot(aes(x = age, y = expected_avg, color = domain)) +
  geom_rect(data = subset(label_df, label == "social"), aes(fill = label), color = NA, alpha = .07,
            xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf, show.legend = FALSE) +
  geom_smooth(method = 'lm', formula = y ~ poly(x,2), alpha = .2, se = FALSE, size = 1.25) + 
  scale_y_continuous(breaks = seq(-.2, .45, .2)) +
  coord_cartesian(ylim = c(-.25, .45)) +
  scale_color_manual(values = pal_social_academic) +
  scale_fill_manual(values = "lightgrey") +
  scale_x_continuous(breaks = c(10, 13, 16)) + 
  facet_grid(~ label, labeller = parcel_labeller) +
  labs(x = "\nage", y = "mean predicted BOLD signal value\n",  color = '') +
  dcbw +
  theme(legend.position = c(.85, .15),
        legend.spacing.y = unit(.01, 'cm'),
        legend.margin = unit(0, "cm"))

soc_acad_plot = neuro_plot_data %>%
  group_by(subjectID, age, label, domain, parcellation) %>%
  mutate(expected_avg = mean(expected, na.rm = TRUE)) %>%
  select(subjectID, age, label, domain, expected_avg) %>%
  unique() %>%
  spread(domain, expected_avg) %>%
  mutate(expected_diff = social - academic) %>%
  distinct(parcellation, age, label, .keep_all = T) %>%
  ggplot(aes(x = age, y = expected_diff)) +
  geom_rect(data = subset(label_df, label == "social"), aes(fill = label), alpha = .07,
            xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf, show.legend = FALSE) +
  geom_smooth(aes(group = parcellation, size = label), method = "lm", formula = y ~ poly(x, 2),
              se = FALSE, color = "grey50") +
  geom_smooth(method = 'lm', formula = y ~ poly(x,2), 
              se = FALSE, color = pal_social_academic[2], size = 1.5) + 
  scale_fill_manual(values = "lightgrey") +
  scale_size_manual(values = c(.03, .1, .1)) +
  scale_y_continuous(breaks = seq(-.2, .45, .2)) +
  coord_cartesian(ylim = c(-.25, .45)) +
  scale_x_continuous(breaks = c(10, 13, 16)) + 
  facet_grid(~ label, labeller = parcel_labeller) +
  labs(x = "\nage", y = "mean predicted BOLD signal value\n",  color = '') +
  dcbw +
  theme(legend.position = "none")

(h1_fitted = cowplot::plot_grid(domain_plot, soc_acad_plot,
                                labels = c('A', 'B'), ncol = 2,
                                rel_widths = c(1, 1)))
```

## hypothesis 2
```{r h2_fitted, fig.width=12, fig.height=5}
target_plot = neuro_plot_data %>%
  group_by(subjectID, age, label, target, parcellation) %>%
  mutate(expected_avg = mean(expected_mean, na.rm = TRUE)) %>%
  distinct(parcellation, target, target, age, label, .keep_all = T) %>%
  ggplot(aes(x = age, y = expected_avg, color = target)) +
  geom_rect(data = subset(label_df, label == "self"), aes(fill = label), color = NA, alpha = .07,
            xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf, show.legend = FALSE) +
  geom_smooth(method = 'lm', formula = y ~ poly(x,2), alpha = .2, se = FALSE, size = 1.25) + 
  scale_y_continuous(breaks = seq(-.2, .3, .1)) +
  coord_cartesian(ylim = c(-.2, .35)) +
  scale_color_manual(values = pal_self_other) +
  scale_fill_manual(values = "lightgrey") +
  scale_x_continuous(breaks = c(10, 13, 16)) + 
  facet_grid(~ label, labeller = parcel_labeller) +
  labs(x = "\nage", y = "mean predicted BOLD signal value\n",  color = '') +
  dcbw +
  theme(legend.position = c(.85, .15),
        legend.spacing.y = unit(.01, 'cm'),
        legend.margin = unit(0, "cm"))

self_other_plot = neuro_plot_data %>%
  group_by(subjectID, age, label, target, parcellation) %>%
  mutate(expected_avg = mean(expected, na.rm = TRUE)) %>%
  select(subjectID, age, label, target, expected_avg) %>%
  unique() %>%
  spread(target, expected_avg) %>%
  mutate(expected_diff = self - other) %>%
  distinct(parcellation, age, label, .keep_all = T) %>%
  ggplot(aes(x = age, y = expected_diff)) +
  geom_rect(data = subset(label_df, label == "self"), aes(fill = label), alpha = .07,
            xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf, show.legend = FALSE) +
  geom_smooth(aes(group = parcellation, size = label), method = "lm", formula = y ~ poly(x, 2),
              se = FALSE, color = "grey50") +
  geom_smooth(method = 'lm', formula = y ~ poly(x,2), 
              se = FALSE, color = pal_self_other[2], size = 1.5) + 
  scale_fill_manual(values = "lightgrey") +
  scale_size_manual(values = c(.03, .1, .1)) +
  scale_y_continuous(breaks = seq(-.2, .3, .1)) +
  coord_cartesian(ylim = c(-.2, .35)) +
  scale_x_continuous(breaks = c(10, 13, 16)) + 
  facet_grid(~ label, labeller = parcel_labeller) +
  labs(x = "\nage", y = "mean predicted BOLD signal value\n",  color = '') +
  dcbw +
  theme(legend.position = "none")

(h2_fitted = cowplot::plot_grid(target_plot, self_other_plot,
                                labels = c('A', 'B'), ncol = 2,
                                rel_widths = c(1, 1)))
```

## hypothesis 3
```{r h3_fitted, fig.width=15, fig.height=5}
int_plot = neuro_plot_data %>%
  distinct(parcellation, target, domain, age, label, .keep_all = T) %>%
  ggplot(aes(x = age, y = expected_mean, group = interaction(target, domain), color = domain, linetype = target)) +
  geom_smooth(method = 'lm', formula = y ~ poly(x,2), alpha = 1, se = FALSE, size = 1.25) + 
  scale_y_continuous(breaks = c(-.4, -.2, 0, .2, .4)) +
  coord_cartesian(ylim = c(-.4, .5)) +
  scale_color_manual(values = pal_social_academic) +
  scale_linetype_manual(name = "", values = c("dotted", "solid")) +
  scale_x_continuous(breaks = c(10, 13, 16)) + 
  facet_grid(~ label, labeller = parcel_labeller) +
  labs(x = "\nage", y = "mean predicted BOLD signal value\n",  color = '', linetype = '') +
  guides(linetype = guide_legend(override.aes = list(color = "black"))) +
  dcbw +
  theme(legend.position = c(.75, .15),
        legend.spacing.y = unit(.01, 'cm'),
        legend.margin = unit(.5, "cm"),
        legend.direction = "vertical",
        legend.box = "horizontal")

soc_acad_int_plot = neuro_plot_data %>%
  group_by(subjectID, age, label, target, domain, parcellation) %>%
  mutate(expected_avg = mean(expected, na.rm = TRUE)) %>%
  select(subjectID, age, label, target, domain, expected_avg) %>%
  unique() %>%
  spread(domain, expected_avg) %>%
  mutate(expected_diff = social - academic) %>%
  distinct(parcellation, age, label, .keep_all = T) %>%
  ggplot(aes(x = age, y = expected_diff, color = target)) +
  geom_smooth(aes(group = interaction(parcellation, target), size = label),
              method = "lm", formula = y ~ poly(x, 2), se = FALSE, show.legend = FALSE) +
  geom_smooth(method = 'lm', formula = y ~ poly(x,2), 
              se = FALSE, size = 1.5) + 
  scale_color_manual(values = pal_self_other) +
  scale_size_manual(values = c(.03, .1, .1)) +
  scale_y_continuous(breaks = c(-.4, -.2, 0, .2, .4)) +
  coord_cartesian(ylim = c(-.4, .5)) +
  scale_x_continuous(breaks = c(10, 13, 16)) + 
  facet_grid(~ label, labeller = parcel_labeller) +
  labs(x = "\nage", y = "mean predicted BOLD signal value\n",  color = '') +
  dcbw +
  theme(legend.position = c(.85, .15),
        legend.spacing.y = unit(.01, 'cm'),
        legend.margin = unit(0, "cm"))


self_other_int_plot = neuro_plot_data %>%
  group_by(subjectID, age, label, domain, target, parcellation) %>%
  mutate(expected_avg = mean(expected, na.rm = TRUE)) %>%
  select(subjectID, age, label, domain, target, expected_avg) %>%
  unique() %>%
  spread(target, expected_avg) %>%
  mutate(expected_diff = self - other) %>%
  distinct(parcellation, age, label, .keep_all = T) %>%
  ggplot(aes(x = age, y = expected_diff, color = domain)) +
  geom_smooth(aes(group = interaction(parcellation, domain), size = label),
              method = "lm", formula = y ~ poly(x, 2), se = FALSE, show.legend = FALSE) +
  geom_smooth(method = 'lm', formula = y ~ poly(x,2), 
              se = FALSE, size = 1.5) + 
  scale_color_manual(values = pal_social_academic) +
  scale_size_manual(values = c(.03, .1, .1)) +
  scale_y_continuous(breaks = c(-.4, -.2, 0, .2, .4)) +
  coord_cartesian(ylim = c(-.4, .5)) +
  scale_x_continuous(breaks = c(10, 13, 16)) + 
  facet_grid(~ label, labeller = parcel_labeller) +
  labs(x = "\nage", y = "mean predicted BOLD signal value\n",  color = '') +
  dcbw +
  theme(legend.position = c(.85, .15),
        legend.spacing.y = unit(.01, 'cm'),
        legend.margin = unit(0, "cm"))

(h3_fitted = cowplot::plot_grid(int_plot, soc_acad_int_plot, self_other_int_plot,
                       labels = c('A', 'B', 'C'), ncol = 3))
```
